Supporting Information

### 2018-03-05 SupportingInformation.Rmd
added the main computational work for an analysis of C and N data that looks at deviations from a normal-copula null for multiple locations from the lower to upper tail

### Non-paramtric analysis of tail dependence
<!--Do the intensive part of the analysis-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)

#initialize
npa_res_CN<-data.frame(Statistic=c("Kendall","Spearman","Corl","Coru","CorlmCoru","Corlt0p1","Corgt0p9","Corlt0p1mCorgt0p9","D2l","D2u","D2umD2l","D2lt0p1","D2gt0p9","D2lt0p9mD2gt0p1"),Value=NA,Frac_of_K_surr_gt_val=NA,Frac_of_S_surr_gt_val=NA)

#utility function
calcstats<-function(v)
{
  h1<-Corbds(v[,1],v[,2],0,.5)
  h2<-Corbds(v[,1],v[,2],0.5,1)
  h3<-Corbds(v[,1],v[,2],0,.1)
  h4<-Corbds(v[,1],v[,2],0.9,1)
  h5<-D2bds(v[,1],v[,2],0,.5)
  h6<-D2bds(v[,1],v[,2],0.5,1)
  h7<-D2bds(v[,1],v[,2],0,.1)
  h8<-D2bds(v[,1],v[,2],0.9,1)
  return(c(cor(v[,1],v[,2],method="kendall"),
           cor(v[,1],v[,2],method="spearman"),
           h1,h2,h1-h2,
           h3,h4,h3-h4,
           h5,h6,h6-h5,
           h7,h8,h8-h7
  ))
}

#get value on the real data
npa_res_CN[,"Value"]<-calcstats(v_CN)

#Do the kendall surrogates
cop<-normalCopula(.5,2)
numsurrog<-1000
surv<-copsurrog2d(v_CN,cop,"kendall",numsurrog)
res<-apply(FUN=calcstats,X=surv,MARGIN=3)
for (counter in 1:dim(npa_res_CN)[1])
{
  npa_res_CN[counter,"Frac_of_K_surr_gt_val"]<-sum(res[counter,]>npa_res_CN[counter,"Value"])/numsurrog
}

#Do the spearman surrogates
surv<-copsurrog2d(v_CN,cop,"spearman",numsurrog)
res<-apply(FUN=calcstats,X=surv,MARGIN=3)
for (counter in 1:dim(npa_res_CN)[1])
{
  npa_res_CN[counter,"Frac_of_S_surr_gt_val"]<-sum(res[counter,]>npa_res_CN[counter,"Value"])/numsurrog
}
```

<!--Display the table generated above-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)
knitr::kable(npa_res_CN,caption = "Results of non-parametric tests of tail dependence and asymmetry of tail dependence for the soil C and N dataset. Names of statistics and values on the actual C and N data are listed in the first two columns. The third (respectively, fourth) column is the fraction of Kendall-preserving (respectively, Spearman-preserving) surrogate datasets for which the given statistic is greater than its value on the real data. So if these quantities are smaller than 0.025 the statistic is significantly larger than expected based on null hypotheses of normal copulas; if larger than 0.975, significantly smaller.")
```

>>>>

### Non-paramtric analysis of tail dependence
<!--Do the intensive part of the analysis-->
```{r stat_soilCN_graphic_approach, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)

#utility function
calcstats<-function(v,f,nm)
{
  #calculate the stats
  res<-c(f(v[,1],v[,2],0,.5),
          f(v[,1],v[,2],0.5,1),
          f(v[,1],v[,2],0,.25),
          f(v[,1],v[,2],0.25,.5),
          f(v[,1],v[,2],.5,.75),
          f(v[,1],v[,2],.75,1))
  for (lbd in seq(from=0,to=0.9,by=0.1))
  {
    res<-c(res,f(v[,1],v[,2],lbd,lbd+.1))
  }

  #name the result vector
  h<-paste(nm,c(0,0.5,0,0.25,0.5,0.75,seq(from=0,to=0.9,by=0.1)),"to",
                    c(0.5,1,0.25,0.5,0.75,1,seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-gsub(".","p",h,fixed=T)
  names(res)<-h

  return(res)
}

#Do the kendall surrogates
cop<-normalCopula(.5,2)
numsurrog<-1000
surv_K<-copsurrog2d(v_CN,cop,"kendall",numsurrog)

#Do the spearman surrogates
surv_S<-copsurrog2d(v_CN,cop,"spearman",numsurrog)

#now work with the correlation stats
corstats_d<-calcstats(v_CN,Corbds,"Cor")
corstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Corbds,nm="Cor")
corstats_K<-apply(FUN=quantile,X=corstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))
corstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Corbds,nm="Cor")
corstats_S<-apply(FUN=quantile,X=corstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the D2 stats
D2stats_d<-calcstats(v_CN,D2bds,"Dtwo")
D2stats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_K<-apply(FUN=quantile,X=D2stats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))
D2stats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_S<-apply(FUN=quantile,X=D2stats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the P stats
Pbds_wrap<-function(vi,vj,lb,ub)
{
  return(Pbds(vi,vj,lb,ub)$abs_res)
}
Pstats_d<-calcstats(v_CN,Pbds_wrap,"P")
Pstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Pbds_wrap,nm="P")
Pstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Pbds_wrap,nm="P")
```
